\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{calc} % added
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingNormal}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small #1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubSubheadingLeft}[2]{ % added
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
\end{description}
}

\begin{document}
\begin{center}
  {\Huge \scshape Vuong Ho} \\ \vspace{1pt}
  % 123 Street Name, Town, State 12345 \\ \vspace{1pt}
  \small \raisebox{-0.1\height}
  \faPhone\ (585) 606-0796
  ~ \href{mailto:vuong@vuongho.me}{\raisebox{-0.2\height} \faEnvelope\ \underline{ vuong@vuongho.me }}
   ~ \href{ https://vuongho.me/ }{\raisebox{-0.2\height} \faHome\ \underline{ vuongho.me }} 
   ~ \href{ https://linkedin.com/in/vuongho/ }{\raisebox{-0.2\height} \faLinkedin\ \underline{ in/vuongho }} 
   ~ \href{https://github.com/{'link': 'https://github.com/goodudetheboy/', 'alias': 'goodudetheboy'}}{\raisebox{-0.2\height} \faGithub\ \underline{ goodudetheboy }} 
  \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      { University of Rochester }{ Expected Dec 2025 }
      { MS in Computer Science } {  }
  
    \resumeSubheading
      { University of Rochester }{ May 2024 }
      { BS in Computer Science, BS in Applied Mathematics, Operations Research Certificate } { GPA: 3.79/4.00 }
  
    \resumeSubheading
      { CodePath }{ May – Aug 2022 }
      { Advanced Software Engineering Certificate } { Remote }
  
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      
        \textbf{ Languages }{: Python, Java, JavaScript, Typescript, Flutter, Kotlin, HTML/CSS, SQL, C/C++, C\#} \\
      
        \textbf{ Developer Tools }{: Gradle, Node.js, MongoDB, AWS, Google Cloud Platform, React.js, Jest, JavaCC, Linux, Docker} \\
      
        \textbf{ Frameworks }{: VS Code, Git, ChatGPT, Github Actions, Android Studio, SonarCloud, Elasticsearch, Bash} \\
      
        \textbf{ Collaborative Methodologies }{: Agile, Scrum, DevOps, Test-Driven Development, Slack, Github Projects, Jira} \\
      
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      { Meta \& Major League Hacking }{ Jun 2024 – Present }
      { Site Reliability Engineering Fellow }{ Rochester, NY }
      \resumeItemListStart
      
        \resumeItem{ Chosen as one of the top 2\% out of 2,500 applicants for the elite Meta \& MLH Production Engineering Fellowship. }
      
        \resumeItem{ Developed a Flask project from scratch deployed it on cloud servers with Nginx reverse proxy and SSL certificates. }
      
        \resumeItem{ Leveraged GitHub Actions for CI/CD, test-driven development, and Docker to achieve 90\% faster deployment times. }
      
      \resumeItemListEnd
  
    \resumeSubheading
      { Vietnam Tech Society }{ Jun 2022 – Jan 2023 }
      { Software Engineer Intern }{ Rochester, NY }
      \resumeItemListStart
      
        \resumeItem{ Delivered a robust TypeScript and Firebase project that enables users to configure and filter appointment availability. }
      
        \resumeItem{ Deployed the “Filter by Availability” feature with 100\% test coverage, resulting in a 90\% improvement in usability. }
      
        \resumeItem{ Reduced server cost by 25\% by optimizing backend Firebase functions to operate dynamically rather than periodically. }
      
      \resumeItemListEnd
  
    \resumeSubheading
      { Google Summer of Code 2021 }{ May – Aug 2021 }
      { Software Engineer Intern }{ Rochester, NY }
      \resumeItemListStart
      
        \resumeItem{ Engineered a key feature for OpenStreetMap’s Vespucci Android app that efficiently evaluates input opening hours. }
      
        \resumeItem{ Implemented an evaluator that processes opening hours of 140,000+ locations with Java, Gradle, and Github Actions. }
      
        \resumeItem{ Supported a grammar system of 80+ rules, expanding coverage from 10\% to approximately 100\% of the specification. }
      
      \resumeItemListEnd
  
    \resumeSubheading
      { University of Rochester }{ Sep 2021 – May 2024 }
      { Teaching Assistant }{ Rochester, NY }
      \resumeItemListStart
      
        \resumeItem{ Courses: Artificial Intelligence, Computation \& Formal System, Programming Language, Discrete Mathematics. }
      
        \resumeItem{ Facilitated weekly study sessions for 30 students, focusing on advanced computer science and mathematics concepts. }
      
      \resumeItemListEnd
  
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Technical Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
      {\href{ https://devpost.com/software/vietrochack }{\textbf{SwipeAndFly}} $|$ \emph{ Hyper-personalized trip planning with TikTok videos. }}{ Jun – Aug 2024 }
      \resumeItemListStart
      
        \resumeItem{ Led a team of 5 to create a hyper-personalized trip planning platform tailored to users travel TikTok videos. }
      
        \resumeItem{ Architected and deployed a scalable AWS microservices backend with a Vite frontend, achieving 99.9 uptime and global deployment on Firebase, 40\% faster load times, supported by a Github Actions CI/CD pipeline with 90 test coverage. }
      
        \resumeItem{ Received 150+ likes and votes, the most liked project out of 219 teams, in the TikTok TechJam 2024 hackathon. }
      
      \resumeItemListEnd
      
        \vspace{-13pt}
      
    
      \resumeProjectHeading
      {\href{ https://devpost.com/software/eduvision-y9fw0g }{\textbf{EduVision}} $|$ \emph{ Eye-tracking powered classroom assistance system. }}{ Mar – May 2024 }
      \resumeItemListStart
      
        \resumeItem{ Led a team of 3 in developing a classroom assistance system that utilizes real-time eye-tracking to detect possible confusing topics using students’ gaze heatmap and provide classroom statistics to instructors with their teaching. }
      
        \resumeItem{ Won Best Education Award out of 43 teams at YHack 2024 hackathon hosted Yale University. }
      
      \resumeItemListEnd
      
    
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------AWARDS---------------
\section{Awards}
    \resumeSubHeadingListStart
    
        \resumeSubheadingNormal{\textbf{ YHack 2024 Hackathon at Yale University } | \textit{ Best Education Award }}{ Mar 2024 }
        \vspace{-16pt}
    
        \resumeSubheadingNormal{\textbf{ DandyHacks’23 Hackathon at University of Rochester } | \textit{ Most Dandy Hack Award }}{ Nov 2023 }
        \vspace{-16pt}
    
        \resumeSubheadingNormal{\textbf{ ICPC Northeast North America Regional Contest 2023 } | \textit{ Rank 36/93 }}{ Oct 2023 }
        \vspace{-16pt}
    
        \resumeSubheadingNormal{\textbf{ ICPC Northeast North America Regional Contest 2022 } | \textit{ Rank 15/84 — Bronze Medal }}{ Feb 2023 }
        \vspace{-16pt}
    
    \resumeSubHeadingListEnd

\end{document}